### 2016-06-11 sec1_introduction.tex
Checkpoint
Saved algo part

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
 & {\tiny Proximity} & {\tiny Consecutiveness} & {\tiny Time Complexity}\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|(M + log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & - & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
\end{tabular} 
\caption{Constraints and complexity of co-movement patterns. The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
\label{tbl:existing_co_patterns}
\end{table}

@@

The other issue with existing methods is that they are built on top of centralized indexes which may not be scalable. Table~\ref{tbl:existing_co_patterns} shows their theoretical complexities in the worst cases and the largest real dataset ever evaluated in previous studies is up to million-scale points collected from hundreds of moving objects. In practice, the dataset is of much higher scale and the scalability of existing methods is left unknown. Thus, we conduct an experimental evaluation with $4000$ objects moving for $2500$ timestamps to examine the scalability. Results in Figure~\ref{fig:related_work_scalability} show that their performances degrade dramatically as the dataset scales up. For instance,
the detection time of \emph{swarm} drops five times as the number of objects grows from \emph{1k} to \emph{2k}. Similarly,
the performance of \emph{group} drops over seven times as the number of snapshots grows from \emph{1.4k} to \emph{2.4k}.
These observations imply that existing methods are not scalable to support large-scale trajectory databases.

%It is easy to spot that none of the existing solutions are scalable to handle large-scale trajectories which include near billions of data points.
%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
%Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{$1k$ objects}
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{$1.2k$ timestamps}
    \label{fig:fig2}
    \end{subfigure}
    \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
    is used with up two 2.4 million data points.}
    \label{fig:related_work_scalability}
\end{figure}

@@

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining. Section~\ref{sec:system_overview} provides an overview of our parallel architecture. Solutions to mining the general co-movement patterns are presented in Section~\ref{sec:trm_solution} and Section~\ref{sec:spm_solution}. Section~\ref{sec:optimization} discusses various optimization techniques to boost the system performance; Section~\ref{sec:experiment} conducts extensive experiments to verify the usefulness and efficiency of our system. Finally Section~\ref{sec:conclusion} concludes the paper.

>>>>

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
Patterns & {\tiny Proximity} & {\tiny Consecutiveness} & {\tiny Time Complexity}\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|(M + log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & - & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
\end{tabular} 
\caption{Constraints and complexity of co-movement patterns. The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
\label{tbl:existing_co_patterns}
\end{table}

@@

The other issue with existing methods is that they are built on top of centralized indexes which may not be scalable. Table~\ref{tbl:existing_co_patterns} shows their theoretical complexities in the worst cases and the largest real dataset ever evaluated in previous studies is up to million-scale points collected from hundreds of moving objects. In practice, the dataset is of much higher scale and the scalability of existing methods is left unknown. Thus, we conduct an experimental evaluation with $4000$ objects moving for $2500$ timestamps to examine the scalability. Results in Figure~\ref{fig:related_work_scalability} show that their performances degrade dramatically as the dataset scales up. For instance, the detection time of \emph{group} drops twenty times as the number of objects grows from \emph{1k} to \emph{4k}. Similarly,
the performance of \emph{swarm} drops over fifteen times as the number of snapshots grows from \emph{1k} to \emph{2.5k}.
These observations imply that existing methods are not scalable to support large-scale trajectory databases.

%It is easy to spot that none of the existing solutions are scalable to handle large-scale trajectories which include near billions of data points.
%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
%Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{$1k$ timestamps}
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{$1k$ objects}
    \label{fig:fig2}
    \end{subfigure}
    \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
    is used with up two 2.4 million data points. Default parameters are $M=10$ $K=20$ $L=10$.}
    \label{fig:related_work_scalability}
\end{figure}

@@

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining. Section~\ref{sec:trm} provides a naive \emph{temporal replication and mining} solution. An advanced solution named
\emph{star partition and mining} is presented in Section~\ref{sec:spm}. Section~\ref{sec:opt} discusses various optimization techniques. Section~\ref{sec:exp} conducts extensive experiments to verify the usefulness and efficiency of our system. Finally Section~\ref{sec:concl} concludes the paper.

### 2016-06-11 sec4_baseline.tex
Checkpoint
Saved algo part

\section{Temporal Replication and Mining}
\label{sec:trm}
We resort to the MapReduce (MR) paradigm for designing 
a parallel solution in mining GCMP. It is straightforward 
to partition the trajectory database into equal-sized 
temporal segments; and then mining the GCMP patterns out of each segments. However, GCMP
patterns may cross multiple temporal segments. In order to ensure
the correctness of results, we need to guarantee that
every valid patterns can be mined within at least 
one partitions.
Thus, some snapshots need to be 
replicated several times in multiple partitions. This
leads us to design the \emph{Temporal Replication and Mining}
(TRM) algorithm.

@@

\begin{example}
We illustrate the entire TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=2, L = 2, G=2$. 
In Figure~\ref{fig:trm} (c), snapshots are combined into partitions with sizes equal to 
$(\lceil \frac{K}{L} \rceil-1) *G+2K = 4$. Then a line sweep method is performed in (d) 
for partition $1$. Each $C_i$ refers to the candidate set during sweeping snapshot $i$. 
Initially, $C_1$ contains patterns whose object set is in snapshot $1$.
As line sweeps, at snapshot $4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
are both $\{1,2,4\}$ which violate the $G$ constraint, 
thus the two candidates are removed from $C_4$. After all snapshots are swept, 
$\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

>>>>

\section{Temporal Replication and Mining}
\label{sec:trm}
We resort to the MapReduce (MR) paradigm for designing 
a scalable parallel solution in mining GCMP. It is straightforward 
to partition the trajectory database into equal-sized 
temporal segments; and then mining the GCMP patterns out of each segments. However, GCMP
patterns may cross multiple temporal segments. To ensure
the correctness, we need to guarantee that
every valid pattern can be mined within at least 
one partitions.
Thus, some snapshots need to be 
replicated several times in multiple partitions. This
leads us to design the \emph{Temporal Replication and Mining}
(TRM) algorithm.

@@

\begin{example}
We illustrate the work flow of  TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=2, L = 2, G=2$. 
In Figure~\ref{fig:trm} (c), snapshots are combined into partitions with sizes equal to 
$(\lceil \frac{K}{L} \rceil-1) *G+2K = 4$. Then a line sweep method is performed in (d) 
for partition $1$. Each $C_i$ refers to the candidate set during sweeping snapshot $i$. 
Initially, $C_1$ contains patterns whose object set is in snapshot $1$.
As line sweeps, at snapshot $4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
are both $\{1,2,4\}$ which violate the $G$ constraint, 
thus the two candidates are removed from $C_4$. After all snapshots are swept, 
$\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

### 2016-06-11 sec5_spm.tex
Checkpoint
Saved algo part

\section{Star Partition and Mining}
\label{sec:spm_solution}
TRM approach requires to replicate entire
trajectories $O(|\mathbb{T}|)$ times, which is inefficient
in parallelism. To overcome this limitation, we 
propose the \emph{Star Partition and Mining} (SPM) method.
In SPM, we design a graph model, named \emph{connection graph}, to capture 
the co-moving behavior among objects. In such a way, 
given an object $u$, all the objects potentially
co-moved with $u$ are captured in $u$'s neighborhood, which
forms a \emph{star} structure in graph terms. SPM utilizes
such structures to partition objects and then adapts an Apriori 
algorithm to discover true GCMPs from each partition.

@@

\begin{algorithm}
\caption{Apriori Mining}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State { Lv $\gets \{\}$,Ground $\gets \{\}$, Output $\gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$}
\State Ground.add($\langle \{s,t\}, T \rangle$);
\State Lv $\gets$ Ground;
\EndFor
\While{true}
	\If{Lv is not empty} 
		\State{LvCand $\gets \{\}$ }
		\ForAll{$cand_v \in Lv$}
			\ForAll{$cand \in $Ground}
				\State $p \gets cand_v$ join $cand$
				\If{$p.T$ is a candidate sequence} 
					\State LvCand.add($p$)
				\EndIf
			\EndFor
		\EndFor
		\If{$Lv$ is a pattern}
			\State{Output.add($Lv$)}
			\State{break}			 
		\EndIf
		\State {Lv $\gets$ LvCand}
	\Else
		\State{break}
	\EndIf
\EndWhile
\State output.addAll($Lv$)
\State \Return output
\end{algorithmic}
\end{algorithm}

@@

\subsubsection{Optimal Star Partition}
An important concern in design parallel algorithms is 
the distribution of work loads. Unlike TRM where each partition
contains equal-sized snapshot, the size distribution 
of stars remains SPM unknown. 
Traditionally, the quality of a partition strategy 
is measured based on two aspects: (1) the number of result partition, which
affects the maximum parallelism
(2) the balance of partition sizes, which affects the finishing
time of a job. We notice that, in star partition, the total sizes of 
stars are invariant. Therefore, the quality of a partition strategy
can be formalized as the \emph{skewness}, which is the maximum star size
among all stars. Smaller \emph{skewness} naturally results in more partitions
and less imbalance.

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{star-alt.eps}
\caption{An alternative numbering and partitioning of the connection graph in Figure~\ref{fig:star_partition}.}
\label{fig:star-alt}
\end{figure}

Interestingly, we note that the \emph{skewness} of star partition is affected by
the way the vertexes are numbered in the connection graph. For example,
Figure~\ref{fig:star-alt} gives two valid numbering of vertexes 
in the same connection graph, but produces two different set of stars. 
The upper partitioning constructs four stars with the maximum star consisting of 5 edges.
The lower partitioning constructs five stars with the maximum star consisting of 3 edges.
Apparently the upper partitioning is inferior because its \emph{skewness} is 5 while the
lower one's \emph{skewness} is 3.

Ideally we wish to find a numbering scheme of connection graph
that minimize the \emph{skewness}.
To quantify the objective, we design an linear algebra model as follows: Let $G$ denote a connection graph.
Let $\mathbb{A}$ be an arbitrary numbering of vertexes in $G$.
Let $(A:a_{i,j})$ be a boolean assignment matrix wrt. $\mathbb{A}$ (i.e., $a_{i,j}$ indicates whether vertex $j$ is included in $Sr_i$). Let vector $\vec{b}$
be the \textit{one}\footnote{Every element in $\vec{b}$ is $1$} vector. Let $\vec{c} = A\vec{b}$, then
each $c_i \in \vec{c}$ denotes the size of star for vertex $i$.
Therefore, minimizing the \emph{skewness} can be formulated as follows:
\begin{equation}
\mathbb{A}  = \argmin(||A\vec{b}||_\infty) \text{,where } ||A\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
\end{equation}

@@

\begin{theorem}[Balance of Star Partition]
Let $G$ be a connection graph with $n$ vertexes and the average degree $d$.
Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
For any numbering, $\mathbb{A}$, with high probability, the 
absolute skewness difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
That is, it is very likely that 
$||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
\end{theorem}

\begin{proof}
Let $\mathbb{A}^*$ be the optimal solution wrt Equation 1. Since we have a star
for each object, by the degree-sum formula and pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
Next, let $e_{i,j}$ be an entry in the adjacent matrix of $G$. Note that edges in $G$ are independent. 
Let $d_i$ denote the degree of vertex $i$ in $G$. 
It follows that $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$.
Since in the star partition, each edge is assigned to the vertex
with smaller IDs, the connection between $a_{i,j}$ and $e_{i,j}$ can be written as:
\begin{equation*}
a_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}
There are two observations made on the above equation. First, since $e_{i,j}$s are independent,
$a_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$ are independent. 
$E[a_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.

@@

The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
Next, since the event $(\max_{1\leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
\begin{equation*}
\begin{split}
	Pr(||A\vec{b}||_\infty \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
		& = n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(||A\vec{b}||_\infty \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$. With the observed fact that $||A^*\vec{b}||_\infty \geq d/2$, we conclude that
with probability greater than $(1-1/n)$, 
the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{n\log n})$.
\end{proof}

@@

>>>>

\section{Star Partition and Mining}
\label{sec:spm}
TRM approach requires to replicate entire
trajectories $O(|\mathbb{T}|)$ times, which is inefficient
in parallelism. To overcome this limitation, we 
propose the \emph{Star Partition and Mining} (SPM) method.
In SPM, we design a graph model, named \emph{connection graph}, to capture 
the co-moving behavior among objects. In such a way, 
given an object $u$, all the objects potentially
co-moved with $u$ are captured in $u$'s neighborhood, which
forms a \emph{star} structure in graph terms. SPM utilizes
such structures to partition objects and then adapts an Apriori 
algorithm to discover true GCMPs from each partition.

@@

\begin{algorithm}
\caption{Apriori Mining}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State { Lv $\gets \{\}$,Ground $\gets \{\}$, Output $\gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$}
\State{Simply $e(s,t)$} \Comment{Edge Simplification}
\State {Ground.add($\langle \{s,t\}, T \rangle$)}
\State {Lv $\gets$ Ground}
\EndFor
\While{Lv is not empty}
		\State {Lv $\gets$ Lv $\oplus $ Ground}
		\State {Remove false patterns in Lv}
		\Comment{Temporal Monotonicity}
		\If{union of Lv is a valid patter}
			\State{output.add(Lv)} \Comment{Forward Closure}
			\State{break}
		\EndIf
\EndWhile
\State output.addAll($Lv$)
\State \Return output
\end{algorithmic}
\end{algorithm}

@@

\subsubsection{Optimal Star Partition}
An important concern in design parallel algorithms is 
the distribution of work loads.  
Traditionally, the quality of a partition strategy 
is measured based on two aspects: (1) the number of result partition, which
affects the maximum parallelism
(2) the size balance of partitions, which affects the finishing
time of a job. Unlike TRM where each partition
contains equal-sized snapshots, the size distribution 
of stars in SPM remains unknown.
Nevertheless, we notice that, in SPM, the total sizes of 
stars are invariant. Therefore, the quality of a star partition
can be formalized as the \emph{skewness}, which is the maximum star size
among all stars. Smaller \emph{skewness} naturally results in more partitions
and less imbalance.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{star-alt.eps}
\caption{An alternative numbering and partitioning of the connection graph in Figure~\ref{fig:star_partition}.}
\label{fig:star-alt}
\end{figure}

Interestingly, we note that the \emph{skewness} of star partition is affected by
the way the vertexes are numbered in the connection graph. For example,
Figure~\ref{fig:star-alt} gives two valid numbering of vertexes 
of the same connection graph, but produces two different set of stars. 
The upper partitioning constructs 4 stars with the maximum star consisting of 5 edges.
The lower partitioning constructs 5 stars with the maximum star consisting of 3 edges.
Apparently the upper partitioning is inferior because its \emph{skewness} is 5 while the
lower one's \emph{skewness} is 3.

Ideally we wish to find a numbering scheme of connection graph
that minimize the \emph{skewness}.
To quantify, we use an linear algebra model as follows: 
Let $G$ denote a connection graph.
Let $\mathbb{A}$ be an arbitrary numbering of vertexes in $G$.
Let $(A:a_{i,j})$ be a boolean assignment matrix wrt. $\mathbb{A}$
(i.e., $a_{i,j}$ indicates whether vertex $j$ is included in $Sr_i$). 
Let vector $\vec{b}$ be the \textit{one}\footnote{Every element in $\vec{b}$ is $1$} 
vector. Let $\vec{c} = A\vec{b}$, then each $c_i \in \vec{c}$ 
denotes the size of the star $Sr_i$.
Therefore, minimizing the \emph{skewness} can be formulated as follows:
\begin{equation}
\mathbb{A}  = \argmin(||A\vec{b}||_\infty) \text{,where } ||A\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
\end{equation}

@@

\begin{theorem}[Balance of Star Partition]
Let $G$ be a connection graph with $n$ vertexes and the average degree $d$.
Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
For an random numbering, $\mathbb{A}$, with high probability, the 
absolute skewness difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
That is, it is very likely that 
$||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
\end{theorem}

\begin{proof}
Let $\mathbb{A}^*$ be the optimal numbering wrt Equation 1. Since we have a star
for each object, by the degree-sum formula and pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
Next, let $e_{i,j}$ be an entry in the adjacent matrix of $G$. Note that edges in $G$ are independent. 
Let $d_i$ denote the degree of vertex $i$ in $G$. 
It follows that $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$.
Since in the star partition, each edge is assigned to the vertex
with smaller IDs, the connection between $a_{i,j}$ and $e_{i,j}$ can be written as:
\begin{equation*}
a_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}
There are two observations made on the above equation. First, since $e_{i,j}$s are independent,
$a_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$ are independent. 
$E[a_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.

@@

The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
Next, since the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
\begin{equation*}
\begin{split}
	Pr(||A\vec{b}||_\infty \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
		& = n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute back $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(||A\vec{b}||_\infty \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$. With the observed fact that $||A^*\vec{b}||_\infty \geq d/2$, we conclude that
with probability greater than $(1-1/n)$, 
the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{n\log n})$.
\end{proof}

@@

Utilizing Theorem 3, in SPM, it is safe to choose the object IDs as 
the vertex number. This because in reality, object IDs are often 
hashed and can be deemed as random.
